\documentclass[]{deedy-resume-reversed}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage[hidelinks]{hyperref}

\pagestyle{fancy}
\fancyhf{}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue, % Ensures email and website links are blue
    citecolor=blue,
    allcolors=blue % Forces all links to be blue
}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     TITLE NAME
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\namesection{Shubham Shejul}{
\href{mailto:shejulshubhamdeshmukh@gmail.com}{shejulshubhamdeshmukh@gmail.com} | +91 9923195165 | Pune, Maharashtra
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COLUMN ONE (MAIN SECTION)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.60\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     ABOUT ME
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\textbf{About Me}}
\noindent\rule{\textwidth}{0.4pt}
Software Developer specializing in web development with a strong foundation in full-stack development and modern web technologies. Skilled in JavaScript, React.js, and relational databases.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     INTERNSHIP
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\textbf{Internship}}
\noindent\rule{\textwidth}{0.4pt}

\runsubsection{Software Development Intern}
\hfill
\descript{\href{https://www.zeromoq.com/}{ZeroMOQ}}
\location{| Remote Internship}
\vspace{2pt}

\vspace{8pt}
\begin{tightemize}
\item Built and maintained backend services using Python and Django, ensuring scalable and secure architecture.
\item Integrated AWS S3 for efficient file storage and retrieval, supporting large 3D model files.
\item Collaborated with the founding team and software lead to align product development with business goals.
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\textbf{Projects}}
\noindent\rule{\textwidth}{0.4pt}

\runsubsection{Emprog - Show \& Movie Tracker}
\hfill
\href{https://shejulshubham-app-emprog.netlify.app/}{Live} \hspace{15pt}
\href{https://github.com/ShejulShubham/Emprog}{GitHub}

\vspace{2pt}
\descript{| React.JS, Firebase, TailwindCSS, Zustand}

\vspace{8pt}
\begin{tightemize}
\item Developed a modern web app to track shows, movies, and videos with a clean, responsive interface.
\item Implemented Firebase Authentication with persistent login and protected routes for secure user access.
\item Utilized Zustand for lightweight global state management and seamless integration with Firebase.
\item Designed a mobile-first, responsive UI using TailwindCSS for an optimized user experience.
\end{tightemize}
\sectionsep


\runsubsection{Exrupee - Subscription Tracker}
\hfill
\href{https://shejulshubham-app-exrupee.netlify.app/}{Live} \hspace{15pt}
\href{https://github.com/ShejulShubham/Exrupee.git}{GitHub}

\vspace{2pt}
\descript{| Next.JS, Firebase, FantaCSS}

\vspace{8pt}
\begin{tightemize}
\item Built a real-time subscription tracker using Next.js App Router for seamless page navigation.
\item Integrated Firebase Authentication to handle secure user logins.
\item Implemented Firestore Database to manage and sync subscription data in real-time across sessions.
\end{tightemize}
\sectionsep


\runsubsection{ai.local - Local AI Chatbot System}
\hfill
\href{https://github.com/ShejulShubham/ai.local}{GitHub}

\descript{| Ollama, Docker, Nginx, Open WebUI, WSL}

\vspace{8pt}
\begin{tightemize}
\item Designed and implemented a local AI chatbot system using Ollama.
\item Built dual deployment architectures for Linux and Windows (with WSL), ensuring cross-platform compatibility.
\item Configured Nginx as a reverse proxy to handle client requests and route traffic between the frontend and Ollama.
\end{tightemize}
\sectionsep


\end{minipage}
\hfill
\begin{minipage}[t]{0.33\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\textbf{Education}}
\noindent\rule{\textwidth}{0.4pt}
\subsection{DAC (Web Development)}
\location{Sunbeam Institute of Information Technology}
\descript{2024}
\sectionsep

\subsection{B.Tech (Civil Engineering)}
\location{MIT College of Engineering}
\descript{2020 - 2023}
\sectionsep

\subsection{Diploma (Civil Engineering)}
\location{MIT College of Polytechnic}
\descript{2018 - 2020}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     TECHNICAL SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\textbf{Technical Skills}}
\noindent\rule{\textwidth}{0.4pt}
\subsection{Frameworks \& Libraries}
ReactJS \textbullet{} NodeJS
\sectionsep

\subsection{Databases}
MySQL
\sectionsep

\subsection{Version Control}
Git \textbullet{} GitHub
\sectionsep

\subsection{Programming Languages}
JavaScript (Proficient) \\
Java (Moderate) \\ 
C++ (Basic) \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\textbf{Links} \small{(Click to explore)}}
\noindent\rule{\textwidth}{0.4pt}

\textbf{LinkedIn:} \href{https://www.linkedin.com/in/shejul-shubham}{shejul-shubham} \\
\textbf{GitHub:} \href{https://github.com/shejulshubham}{shejulshubham} \\
\textbf{Portfolio:} \href{https://shejulshubham.github.io/}{shejulshubham.github.io} \\
\textbf{LeetCode:} \href{https://leetcode.com/u/ShejulShubham/}{shejulshubham}

\sectionsep

\end{minipage}
\end{document}
